---
title: "Global Innovation Index App Documentation"
author: "Raul Zambrano"
date: "12/20/2014"
output: html_document
---

This document contains detailed information for the Global Innovation Index (GII) shiny app. The GII 2014 was co-publised by Cornell University, INDEAD and WIPO. For more GII details please visit: 

https://www.globalinnovationindex.org/content.aspx?page=GII-Home.

This a a very simple app that allows users to quickly get the rakings for any of the 143 countries included in GII. 

The user has two options to do this. The first one is to select a country  from a drop down list and obtain the country's GII rank, the actual GII score, as well as its population and GDP per capita.

The second option allows users to select the top N GII ranked countries, N being a number provided by the end user. In this case, the App displays a table of the top N countries in similar format to the first option. Users can also select all countries.

The app uses data furnished to me by Cornell University in XLS format. As this data was not very clean, I did some simple modifications to the original and kept only the first 18 variables which what I needed to develop the App. 

Here is how the clean data looks like:
```{r data}
innov <- read.csv("./GlobalInnovationIndex2014.csv",as.is=c(1:2,6:9))
str(innov)
head(innov,1)
```

To develop the shiny app I wrote a simple R script that reads the data, keeps only the 5 variables I used for the app, renames the variables and creates a list of countries sorted alphabetically which I  used to display the drop down menu for the Select Country option in the shiny App.

Here is the code:
```{r code, results='hide'}
innov <- innov[,c(-2,-4,-6:-9,-11:-13,-15:-17)]
names(innov) <- c("Country","Population","GDPperCap","Rank","Score")
allCtrys <- sort(innov[ , "Country"])
```

The shiny server.R file runs all this from the R script I created, once the App is launched -and only once per session!

That's all folks. Enjoy!














